Pteropod biomarker analysis

### 2018-04-12 biomark.Rmd
no mods with vif > 11, removed CO3 from analysis

envchr <- c('pCO2', 'pH', 'CO3', 'Ara', 'O2', 'Temp', 'Fluor')
ptechr <- c('CAT', 'GR', 'GSHonGSSG', 'GST', 'LPX', 'ORAC', 'SOD', 'ORACvLPX')
```

@@

Pairwise models with interactions for each biomarker

@@

selectInput("mod", "Choose model:", paste0('mod', seq(1:nrow(mods))))

>>>>

envchr <- c('pCO2', 'pH', 'Ara', 'O2', 'Temp', 'Fluor')
ptechr <- c('CAT', 'GR', 'GSHonGSSG', 'GST', 'LPX', 'ORAC', 'SOD', 'ORACvLPX')
```

@@

Pairwise models with interactions for each biomarker, only pairwise models with VIF < 11 are shown

@@

selectInput("mod", "Choose model:", mod_all[['Model']])
